Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-21 draft.tex
more rearrangemetns

>>>>

\subsection{Maps out of enveloping $E_n$ algebras}

These results can be marshaled to prove the following.

\begin{prp}
Let $\Ch_k^{\otimes_k}$ be the symmetric monoidal $\infty$-category arising from cochain complexes of vector spaces over a characteristic zero field $k$.
Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
Then given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
\end{prp}

That is, the forgetful functor $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k} \to \Ch_k^{\otimes_k}$ sends $B_f$ to~$B$.

\begin{proof}
\owen{Essentially, we verify that a bunch of "forgetful functors" are $E_n$-monoidal.}
\end{proof}

By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
As the forgetful functor $\Alg_\Lie(\Ch_k^{\rm dg}) \to \Alg_\Lie(\Ch_k^{\rm dg})$ is \owen{more adjectives},
we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.

\owen{I'd love to say we can produce a map from our favorite model of the envelope, but we may not need it.}
